Reconstructing the last known movements of one of Nature's giants

### 2017-06-23 manuscript/blue-whale-ms.tex
Change references to figures now we are splitting into three
Add CT edits to paragraph 4 main text

% 2 panel figure of the two traces - real and simulated

\begin{figure}
  \centering
    \begin{subfigure}{0.8\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1a-raw-dC-dN-data.png}
      \label{fig1a}
    \end{subfigure}

    \begin{subfigure}{0.8\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1c-migratory-model-d13C.png}
      \label{fig1b}
    \end{subfigure} 
  \caption{Two panel figure with two traces}
\end{figure}

% two panel with the simulations and map
\begin{figure}
  \centering
    \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1b-migratory-model-full-map.png}
      \label{fig2a}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1c-migratory-model-d13C.png}
      \label{fig2b}
    \end{subfigure} 
  \caption{Two panel figure with trace and map}
\end{figure}

% two panel with the simulations and map
\begin{figure}
  \centering
    \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1b-migratory-model-full-map.png}
      \label{figa}
    \end{subfigure}

    \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1c-migratory-model-d13C.png}
      \label{figb}
    \end{subfigure} 
  \caption{Two panel figure with trace and map}
\end{figure}

% two panel with the simulations and map
\begin{figure}
  \centering
    \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1c-migratory-model-d13C.png}
      \label{fig3a}
    \end{subfigure}
    \begin{subfigure}[b]{0.45\textwidth}
      \centering
      \includegraphics[width = \linewidth]{figures/Figure-1b-migratory-model-full-map.png}
      \label{fig3b}
    \end{subfigure} 
  \caption{Two panel figure with trace and map}
\end{figure}

% one panel of the real trace
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-1a-raw-dC-dN-data.png}
  \label{fig11a}
  \caption{One panel figure}
\end{figure}

% one panel of the real trace
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-1b-migratory-model-full-map.png}
  \label{fig11b}
  \caption{One panel figure}
\end{figure}

% one panel of the real trace
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-1c-migratory-model-d13C.png}
  \label{fig11c}
  \caption{One panel figure}
\end{figure}

To interpret these isotopic signatures, we simulated time series of $\delta^{13}$C and $\delta^{15}$N values expected under differing movement behaviours, by coupling a novel agent-based model of whale movements (see Supplementary Methods) to models of global phytoplankton $\delta^{13}$C and $\delta^{15}$N values\cite{magozzi2017using} (Schmittner and Somes). 
We simulated the movement of the whale with the likelihood, direction, and extent of movement influenced by behavioural state, sea surface temperature, water depth and phytoplankton concentration (as a proxy for zooplankton food availability). 
At each time point and location in the simulations, we extracted phytoplankton $\delta^{13}$C and $\delta^{15}$N values from the models\cite{magozzi2017using} (Schmittner and Somes) resulting in a range of simulated isotopic profiles for different migration patterns and foraging areas. 
We then determined which of these simulated profiles were biogeochemically consistent with the isotopic profile of the blue whale's baleen (Fig. 1) and use this to interpret the results.

>>>>

% figure 1
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-1a-raw-dC-dN-data.png}
  \label{fig1}
  \caption{One panel figure}
\end{figure}

% figure 2
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-1b-migratory-model-full-map.png}
  \label{fig2}
  \caption{One panel figure}
\end{figure}

% figure 3
\begin{figure}
  \centering
  \includegraphics[width = \linewidth]{figures/Figure-1c-migratory-model-d13C.png}
  \label{fig3}
  \caption{One panel figure}
\end{figure}

Relating marine animal tissue isotopic compositions to likely locations is complicated by both a lack of spatial reference values and because the isotopic composition of phytoplankton at the base of marine food webs varies in space and time. 
We approach these problems using newly developed, temporally dynamic models of $\delta^{13}$C values in the global ocean\cite{magozzi2017using}, coupled to an agent-based model of whale movements (see Supplementary Methods) to simulate time series of $\delta^{13}$C values expected under differing movement behaviours and in differing parts of the known geographic range of blue whales. 
We then compare simulated profiles with the measured isotopic profile of the blue whale's baleen (Fig. \ref{fig1}) to identify the most likely movement history.
